---
title: "fars tutorial"
author: "Reinhard Simon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This package was built as part of a programming assignment on Coursera.
It provides a set of functions to read and visualize (map) *data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes* (from the assignment text).

# Installation

```{r}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("c5sire/fars")
library(fars)
```

# Basic workflow

Assume that you have downloaded the sample data into your local directory and unzipped them as individual files.

Then you should have three files:

1. accident_2013.csv.bz2
2. accident_2014.csv.bz2
3. accident_2015.csv.bz2

# Principal functions

## Summarize years

```{r}
#fyears = 2013:2015
#fars_summarize_years(fyears)
```


## Visualize fatalities

```{r}
#fars_map_state(11, 2013)
```





